How do changes in ex vary between countries?

### 2022-03-08 draft_paper.Rmd
run and compare best breakpoint with no break (null) model

hmd_ex_selected_countries_with_synth %>%
  filter(year >= 1979) %>% 
  group_by(code, x, sex) %>% 
  nest() %>% 
  mutate(
    best_tau = map_dbl(data, get_best_tau_from_gridsearch)
  )

>>>>

compare_best_breakmodel_with_null <- 
  hmd_ex_selected_countries_with_synth %>%
    filter(year >= 1979) %>% 
    group_by(code, x, sex) %>% 
    nest() %>% 
    mutate(
      best_tau = map_dbl(data, get_best_tau_from_gridsearch)
    ) %>% 
    mutate(
      model_null = map(
        data, 
        ~ .x %>% 
          arrange(year) %>% 
          mutate(delta_ex = ex - lag(ex)) %>% 
          filter(!is.na(delta_ex)) %>% 
          lm(delta_ex ~ 1, data = .)
      )
    ) %>% 
    mutate(
      model_alt = map2(
        best_tau, data,
      ~ .y %>% 
        arrange(year) %>% 
        mutate(delta_ex = ex - lag(ex)) %>% 
        filter(!is.na(delta_ex)) %>% 
        mutate(T_param = ifelse(year < .x, FALSE, TRUE)) %>% 
        lm(delta_ex ~ T_param, data = .)
      )
    )

compare_best_breakmodel_with_null %>% 
  mutate(
    aic_alt  = map_dbl(model_alt, AIC),
    aic_null = map_dbl(model_null, AIC)
  ) %>% 
  mutate(
    alt_preferred = map2_lgl(aic_alt, aic_null, ~ifelse(.x < .y, TRUE, FALSE))
  )
